hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2024-12-04 inst/manuscript/paper.Rmd
add sturgeon model

```{r, eval=FALSE}
smallmouth <- matrix(NA, 10, 2) |> tibble()
colnames(smallmouth) <- c("hours", "temp_F")
smallmouth$hours <- c(52, 54, 70, 78, 90, 98, 150, 167, 238, 234)
smallmouth$temp_F <- c(77, 75, 71, 70, 67, 65, 60, 59, 55, 55)

@@

plot(smallmouth$days~smallmouth$temp_C)

smb_mod <- fit_model(smallmouth,
                     temp = smallmouth$temp_C,
                     days = smallmouth$hours)

@@

Use woody \_example from website

>>>>

```{r, eval=FALSE}
#### temp regime
set.seed(1234)
# create random temps and corresponding dates
temps_sim <- sort(rnorm(n =30, mean = 16, sd = 1), decreasing = TRUE)
dates_sim <-  seq(from = ymd("2000-07-01"),
             to = ymd("2000-07-31"), length.out = 30)

data_sim <- cbind (dates_sim, temps_sim) |> data.frame()

### smallmouth
smallmouth <- matrix(NA, 10, 2) |> tibble()
colnames(smallmouth) <- c("hours", "temp_F")
smallmouth$hours <- c(52, 54, 70, 78, 90, 98, 150, 167, 238, 234)
smallmouth$temp_F <- c(77, 75, 71, 70, 67, 65, 60, 59, 55, 55)

@@

smb_mod <- fit_model(smallmouth,
                     temp = smallmouth$temp_C,
                     days = smallmouth$days,
                     species = "smb",
                     dev.type = "hatch")

### catfish example from Small and Bates 2001
### Effect of Low-Temperature Incubation of Channel Catfish Ictalarus punctatus
### Eggs on Development, Survival, and Growth
### Journal of the World Aquaculture Society

catfish <- matrix(NA, 3, 2) |> tibble()
colnames(catfish) <- c("days", "temp_C")
catfish$days <- c(16,21,26)
catfish$temp_C <- c(22,10,7)

cat_mod <- fit_model(catfish,
                     temp = catfish$temp_C,
                     days = catfish$days,
                     species = "catfish",
                     dev.type = "hatch")

### lake sturgeon mod
### Smith and King 2005
### Dynamics and extent of larval lake sturgeon Acipenser fulvescens drift in the 
### Upper Black River, Michigan
### Journal of Applied Ecology

sturgeon <-  matrix(NA, 7, 2) |> tibble()
colnames(sturgeon) <- c("days", "CTU")
sturgeon$days <- c(7,5,6,6,5,11,7)
sturgeon$CTU <- c(58.1, 62.2, 61.1, 57.5, 58.1, 71.4, 54.7)

sturgeon <- sturgeon |> 
  mutate(temp_C = CTU/days)

plot(sturgeon$days ~ sturgeon$temp_C)

sturgeon_mod <- fit_model(df = sturgeon,
                          days = sturgeon$days,
                          temp = sturgeon$temp_C,
                          species = "sturgeon",
                          dev.type = "hatch")

### predict_phenology

catfish_res <- predict_phenology(data = data_sim,
                  dates = dates_sim,
                  temperature = temps_sim,
                  spawn.date = "2000-07-01",
                  model = cat_mod$func)

# note that 16 C is pretty far out of range of temps for model fit, not best practice
sturgeon_res <- predict_phenology(data = data_sim,
                  dates = dates_sim,
                  temperature = temps_sim,
                  spawn.date = "2000-07-01",
                  model = sturgeon_mod$func)

catfish_res$days2done; sturgeon_res$days2done
```

@@

Use woody example from website
